---
title: "Effect of Recommendation Threshold"
author: "Johannes Nakayama"
date: "14 9 2020"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---






## Setup

For this analysis, the following packages were used: `tidyverse`, `magrittr`, `ggpubr`, `igraph`, `viridis`. Some additional functions to support the work flow and reduce code complexity were written. They are located in the script `helpers.R`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# load libraries ---
library(tidyverse)
library(magrittr)
library(ggpubr)
library(igraph)
library(viridis)

# process / load data ---
if (!("data.RData" %in% list.files())) {source("data_processing.R")}
load("data.RData")

# load helper functions ---
source(file.path("..", "helpers.R"))

# plot specifications ---
SAVE <- TRUE
EXPERIMENT_PREFIX <- "main_tickrec"
RESOLUTION_DPI <- 300
THEME_DESIGN <- 2
plot_no <- 0

# create directories ---
dir.create("graphics", showWarnings = FALSE)
dir.create(file.path("graphics", "pdf"), showWarnings = FALSE)
dir.create(file.path("graphics", "png"), showWarnings = FALSE)
```






## Datasets

The following code reads all the required datasets and formats them according to the requirements of the visualizations. This should result in the following datasets:

  * `config`: all the configurations of the simulations [dataframe]
  * `summary_statistics`: summary statistics on all simulation runs [dataframe]
  * `summary_statistics_aggregated`: summary statistics on all simulation runs aggregated by replicate [dataframe]
  * `mdata`: model data of all simulation runs [dataframe]
  * `mdata_long`: model data of all simulation runs in long format [dataframe]
  * `mdata_summarized`: model data of all simulation runs summarized by replicate [dataframe]
  * `mdata_summarized_long`: model data of all simulation runs summarized by replicate in long format [dataframe]
  * `summary_agent_states`: summary of the agent states over simulation time [dataframe]

```{r inspect-datasets, eval=FALSE}
config
mdata
mdata_long
mdata_summarized
mdata_summarized_long
summary_statistics
summary_statistics_aggregated
summary_agent_states
```






## General Remarks

There are two concepts of time in the following analysis: steps and days. In the model implementation, ten steps form one day. In the analysis, the data have been aggregated where appropriate.

In many of the code blocks, the datasets are slightly modified to be suitable for visualization. These temporary datasets are named `tmp`. 

There are two ways in which the dynamics of the epidemics are displayed: either as new cases per day or as count of agents that are infectious that day (or step respectively).  

All but one factor, all configuration setups have been held constant for the experiments in this analysis. The default values are:
  
  * `Nodes`: 300
  * `N0`: `3
  * `K`: 3
  * `AgentCount`: 1000
  * `TransmissionProb`: 0.05
  * `TestProb`: 0.8
  * `QuarantineDuration`: 140
  * `BehaviorReductionFactor`: 0.25
  * `BehaviorActivated`: TRUE
  * `TickAuthorityPolicy`: 1001
  * `PublicSpaces`: 100
  * `InitialInfectives`: 5
  * `Iterations`: 1000

The factor `TickAuthorityRecommendation` has been sampled from [0, 300] in steps of 20, yielding 16 different configurations. 10 replicates have been run for each configuration.






## Key Statistics

There are four key statistics that I computed for all configurations of the experiment: 
  
  * *peak infective fraction:* peak fraction agents that are infective at the same time
  * *tick of peak infective count:* point in (simulation) time where the peak infective count is reached
  * *duration of the epidemic:* time between the start of the simulation and the recovery of the last infective agent (in ticks)
  * *fraction of agents still susceptible after the simulation:* the fraction of agents that have never been infected during the entire simulation

The aim of the analysis is to see if there are trends and differences between the configurations. 

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "epidemic_peak")
width <- 7
height <- 5
labs <- c(
  title = "Effect of step of recommendation on epidemic peak",
  x = "Step of recommendation", 
  y = "Peak fraction of infective agents",
  caption = "Dots indicate the mean, error bars the standard error."
)

# plotting ---
summary_statistics_aggregated %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = PeakInfectiveFractionMean)) +
    geom_line() +
    geom_point(size = 2) +
    geom_errorbar(
      aes(
        ymin = PeakInfectiveFractionMean - PeakInfectiveFractionSE, 
        ymax = PeakInfectiveFractionMean + PeakInfectiveFractionSE
      ),
      width = 10
    ) +
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.05), limit = c(0.6, 1)) +
    labs(title = labs["title"], x = labs["x"], y = labs["y"], caption = labs["caption"]) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

# reset ---
rm(filename, height, labs, width)
```

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "step_of_peak")
width <- 7
height <- 5
labs <- c(
  title = "Effect of step of recommendation on step of epidemic peak",
  x = "Step of recommendation", 
  y = "Step of epidemic peak",
  caption = "Dots indicate the mean, error bars the standard error."
)

# plotting ---
summary_statistics_aggregated %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = TickOfPeakInfectiveCountMean)) +
    geom_line() +
    geom_point(size = 2) +
    geom_errorbar(
      aes(
        ymin = TickOfPeakInfectiveCountMean - TickOfPeakInfectiveCountSE, 
        ymax = TickOfPeakInfectiveCountMean + TickOfPeakInfectiveCountSE
      ),
      width = 10
    ) +
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1000, by = 5), limits = c(190, 250)) +
    labs(title = labs["title"], x = labs["x"], y = labs["y"], caption = labs["caption"]) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

rm(filename, height, labs, width)
```

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "epidemic_duration")
width <- 7
height <- 5
labs <- c(
  title = "Effect of step of recommendation on duration of epidemic",
  x = "Step of recommendation", 
  y = "Duration of epidemic",
  caption = "Dots indicate the mean, error bars the standard error." 
)

# plotting ---
summary_statistics_aggregated %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = DurationOfEpidemicMean)) +
    geom_line() +
    geom_point(size = 2) +
    geom_errorbar(
      aes(
        ymin = DurationOfEpidemicMean - DurationOfEpidemicSE, 
        ymax = DurationOfEpidemicMean + DurationOfEpidemicSE
      ),
      width = 10
    ) +  
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1000, by = 50), limits = c(650, 1000)) +
    labs(title = labs["title"], x = labs["x"], y = labs["y"], caption = labs["caption"]) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

# reset ---
rm(filename, height, labs, width)
```

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "fraction_susceptibles")
width <- 7
height <- 5
labs <- c(
  title = "Effect of step of recommendation on fraction of remaining susceptibles",
  x = "Step of recommendation", 
  y = "Fraction of susceptibles",
  caption = "Dots indicate the mean, error bars the standard error."
)

# plotting ---
summary_statistics_aggregated %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = FractionStillSusceptibleMean)) +
  geom_line() +
  geom_point(size = 2) +
  geom_errorbar(
    aes(
      ymin = FractionStillSusceptibleMean - FractionStillSusceptibleSE, 
      ymax = FractionStillSusceptibleMean + FractionStillSusceptibleSE
    ),
    width = 10
  ) +
  scale_x_continuous(breaks = seq(0, 300, by = 20)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.005), limits = c(0, 0.02)) +
  labs(title = labs["title"], x = labs["x"], y = labs["y"], caption = labs["caption"]) +
  theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
  NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

# reset ---
rm(filename, height, labs, width)
```

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "main_effects")
width <- 9
height <- 6
  
# plotting p1 ---
summary_statistics_aggregated %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = PeakInfectiveFractionMean)) +
    geom_line() +
    geom_point(size = 1) +
    geom_errorbar(
      aes(
        ymin = PeakInfectiveFractionMean - PeakInfectiveFractionSE, 
        ymax = PeakInfectiveFractionMean + PeakInfectiveFractionSE
      ),
      width = 0
    ) +
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.05), limit = c(0.6, 1)) +
    labs(
      title = "Effect on epidemic peak",
      x = "Step of recommendation", 
      y = "Peak fraction of infective agents"
    ) +
    theme_thesis(plot_margin = 10, design = THEME_DESIGN) +
    theme(
      plot.title = element_text(size = 12, margin = margin(b = 10)),
      plot.margin = margin(t = 10, b = 10, l = 20, r = 10),
      axis.title.x = element_text(size = 9, margin = margin(t = 5)),
      axis.title.y = element_text(size = 9, margin = margin(r = 5)),
      axis.text.x = element_text(size = 7),
      axis.text.y = element_text(size = 7)
    ) +
    NULL -> p1

# plotting p2 ---
summary_statistics_aggregated %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = TickOfPeakInfectiveCountMean)) +
    geom_line() +
    geom_point(size = 1) +
    geom_errorbar(
      aes(
        ymin = TickOfPeakInfectiveCountMean - TickOfPeakInfectiveCountSE, 
        ymax = TickOfPeakInfectiveCountMean + TickOfPeakInfectiveCountSE
      ),
      width = 0
    ) +
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1000, by = 10), limits = c(190, 250)) +
    labs(
      title = "Effect on step of epidemic peak",
      x = "Step of recommendation", 
      y = "Step of epidemic peak"
    ) +
    theme_thesis(plot_margin = 10, design = THEME_DESIGN) +
    theme(
      plot.title = element_text(size = 12, margin = margin(b = 10)),
      plot.margin = margin(t = 10, b = 10, l = 20, r = 10),
      axis.title.x = element_text(size = 9, margin = margin(t = 5)),
      axis.title.y = element_text(size = 9, margin = margin(r = 5)),
      axis.text.x = element_text(size = 7),
      axis.text.y = element_text(size = 7)
    ) +
    NULL -> p2

# plotting p3 ---
summary_statistics_aggregated %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = DurationOfEpidemicMean)) +
    geom_line() +
    geom_point(size = 1) +
    geom_errorbar(
      aes(
        ymin = DurationOfEpidemicMean - DurationOfEpidemicSE, 
        ymax = DurationOfEpidemicMean + DurationOfEpidemicSE
      ),
      width = 0
    ) +  
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1000, by = 50), limits = c(650, 1000)) +
      labs(
        title = "Effect on duration of epidemic",
        x = "Step of recommendation", 
        y = "Duration of epidemic"
      ) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    theme(
      plot.title = element_text(size = 12, margin = margin(b = 10)),
      plot.margin = margin(t = 10, b = 10, l = 20, r = 10),
      axis.title.x = element_text(size = 9, margin = margin(t = 5)),
      axis.title.y = element_text(size = 9, margin = margin(r = 5)),
      axis.text.x = element_text(size = 7),
      axis.text.y = element_text(size = 7)
    ) +
    NULL -> p3

# plotting p4 ---
summary_statistics_aggregated %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = FractionStillSusceptibleMean)) +
    geom_line() +
    geom_point(size = 1) +
    geom_errorbar(
      aes(
        ymin = FractionStillSusceptibleMean - FractionStillSusceptibleSE, 
        ymax = FractionStillSusceptibleMean + FractionStillSusceptibleSE
      ),
      width = 0
    ) +
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.005), limits = c(0, 0.02)) +
    labs(
      title = "Effect on fraction of remaining susceptibles",
      x = "Step of recommendation", 
      y = "Fraction of susceptibles"
    ) +
    theme_thesis(plot_margin = 10, design = THEME_DESIGN) +
    theme(
      plot.title = element_text(size = 12, margin = margin(b = 10)),
      plot.margin = margin(t = 10, b = 10, l = 20, r = 10),
      axis.title.x = element_text(size = 9, margin = margin(t = 5)),
      axis.title.y = element_text(size = 9, margin = margin(r = 5)),
      axis.text.x = element_text(size = 7),
      axis.text.y = element_text(size = 7)
    ) +
    NULL -> p4

# arranging plots ---
ggarrange(p1, p2, p3, p4, labels = c("A", "B", "C", "D"), hjust = -0.3, vjust = 0.5) %>% 
  annotate_figure(
    bottom = text_grob(
      "The effects of the timing of the recommendation.\nDots indicate the mean, error bars the standard error.", 
      size = 8, hjust = 1, x = 1
    )
  ) +
  theme_thesis_arrange(plot_margin = 15, design = THEME_DESIGN)

# saving ---
save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)

# reset ---
rm(filename, height, p1, p2, p3, p4, width)
```






## Key Statistics (Detailed)

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "epidemic_peak_detailed")
width <- 7
height <- 5
labs <- c(
  title = "Effect of step of recommendation on epidemic peak",
  x = "Step of recommendation", 
  y = "Peak fraction of infective agents"
)

# plotting ---
summary_statistics %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = PeakInfectiveFraction)) +
    geom_point(size = 2, alpha = 0.2) +
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.05), limits = c(0.55, 1)) +
    labs(title = labs["title"], x = labs["x"], y = labs["y"]) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

# reset ---
rm(filename, height, labs, width)
```

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "step_of_peak_detailed")
width <- 7
height <- 5
labs <- c(
  title = "Effect of step of recommendation on step of epidemic peak",
  x = "Step of recommendation", 
  y = "Step of epidemic peak"
)

# plotting ---
summary_statistics %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = TickOfPeakInfectiveCount)) +
    geom_point(size = 2, alpha = 0.2) +
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1000, by = 10), limits = c(170, 280)) +
    labs(title = labs["title"], x = labs["x"], y = labs["y"]) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

rm(filename, height, labs, width)
```

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "epidemic_duration_detailed")
width <- 7
height <- 5
labs <- c(
  title = "Effect of step of recommendation on duration of epidemic",
  x = "Step of recommendation", 
  y = "Duration of epidemic"
)

# plotting ---
summary_statistics %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = DurationOfEpidemic)) +
    geom_point(size = 2, alpha = 0.2) +
    scale_x_continuous(breaks = seq(0, 300, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1000, by = 50), limits = c(550, 1000)) +
    labs(title = labs["title"], x = labs["x"], y = labs["y"]) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

# reset ---
rm(filename, height, labs, width)
```

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "fraction_susceptibles_detailed")
width <- 7
height <- 5
labs <- c(
  title = "Effect of step of recommendation on fraction of remaining susceptibles",
  x = "Step of recommendation", 
  y = "Fraction of susceptibles"
)

# plotting ---
summary_statistics %>% 
  ggplot(aes(x = TickAuthorityRecommendation, y = FractionStillSusceptible)) +
  geom_point(size = 2, alpha = 0.2) +
  scale_x_continuous(breaks = seq(0, 300, by = 20)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.005), limits = c(0, 0.03)) +
  labs(title = labs["title"], x = labs["x"], y = labs["y"]) +
  theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
  NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

# reset ---
rm(filename, height, labs, width)
```






# Epidemic Curves by Behavior Reduction Factor

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "i_curves")
width <- 8
height <- 7

# data formatting ---
mdata_summarized_long %>% 
  filter(Concept == "ICountLower" | Concept == "ICountUpper") %>% 
  right_join(config %>% select(Config, TickAuthorityRecommendation), by = "Config") %>% 
  filter(TickAuthorityRecommendation >= 100 & TickAuthorityRecommendation <= 200) %>% 
  group_by(TickAuthorityRecommendation, Step) %>% 
  summarize(MeanFraction = mean(Fraction)) %>% 
  ungroup() -> tmp1

tmp1$TickAuthorityRecommendation %<>% factor(levels = seq(100, 200, by = 20))

mdata_summarized_long %>% 
  filter(Concept == "ICumulativeLower" | Concept == "ICumulativeUpper") %>% 
  right_join(config %>% select(Config, TickAuthorityRecommendation), by = "Config") %>% 
  filter(TickAuthorityRecommendation >= 100 & TickAuthorityRecommendation <= 200) %>% 
  group_by(TickAuthorityRecommendation, Step) %>% 
  summarize(MeanFraction = mean(Fraction)) %>% 
  ungroup() -> tmp2

tmp2$TickAuthorityRecommendation %<>% factor(levels = seq(100, 200, by = 20))

# plotting ---
tmp1 %>% 
  ggplot(aes(x = Step, y = MeanFraction, color = TickAuthorityRecommendation)) +
    geom_line(size = 2, alpha = 0.6) +
    scale_x_continuous(breaks = seq(0, 1000, by = 100), limits = c(0, 1000)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.2), limits = c(0, 1)) +
    scale_color_viridis_d(option = "magma") +
    labs(
      title = "Infective curves", 
      x = "Step", 
      y = "Fraction of agents"
    ) +
    guides(color = guide_legend(title = "Step of recommendation", reverse = TRUE)) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    theme(legend.title = element_text()) +
    NULL -> p1

tmp2 %>% 
  ggplot(aes(x = Step, y = MeanFraction, color = TickAuthorityRecommendation)) +
    geom_line(size = 2, alpha = 0.6) +
    scale_x_continuous(breaks = seq(0, 1000, by = 100), limits = c(0, 1000)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.2), limits = c(0, 1)) +
    scale_color_viridis_d(option = "magma") +
    labs(
      title = "Infective curves (cumulated)", 
      x = "Step", 
      y = "Fraction of agents"
    ) +
    guides(color = guide_legend(title = "Step of recommendation", reverse = TRUE)) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    theme(legend.title = element_text()) +
    NULL -> p2

# arrange plots ---
ggarrange(p1, p2, labels = c("A", "B"), ncol = 1, common.legend = TRUE, legend = "right") %>% 
  annotate_figure(bottom = text_grob("Aggregations over all replicates", size = 8, hjust = 1, x = 1)) +
  theme_thesis_arrange(plot_margin = 15, design = THEME_DESIGN)

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

# reset ---
rm(filename, height, tmp, width)
```






## Contagion Dynamics

```{r}
# generics ---
plot_no <- plot_no + 1
filename <- paste0(EXPERIMENT_PREFIX, "_", stringr::str_pad(plot_no, 2, "left", "0"), "_", "contagion")
width <- 8
height <- 8
labs <- c(
  title = "New cases per day", 
  x = "Day", 
  y = "Fraction of agents",
  caption = "New cases per day split by start of the recommendation (aggregated over all replicates).\nThe red dashed lines indicate the start of the recommendation."
)

# data formatting ---
mdata_long %>% 
  inner_join(config %>% select(Config, TickAuthorityRecommendation), by = "Config") %>% 
  select(-Config, -Step) %>% 
  filter(Concept == "NewCasesReal") %>% 
  group_by(TickAuthorityRecommendation, Replicate, Day, Concept) %>%
  summarize(Fraction = sum(Fraction)) %>%
  ungroup() %>% 
  group_by(TickAuthorityRecommendation, Day) %>% 
  summarize(Fraction = mean(Fraction)) %>% 
  ungroup() %>% 
  filter(TickAuthorityRecommendation <= 200 & TickAuthorityRecommendation %% 40 == 0) -> tmp

# plotting ---
tmp %>% 
  ggplot(aes(x = Day)) +
    geom_bar(aes(y = Fraction), stat = "identity", width = 0.5) +
    geom_vline(aes(xintercept = TickAuthorityRecommendation / 10), color = "red", linetype = "dashed", size = 0.7) +
    facet_wrap(. ~ TickAuthorityRecommendation / 10, ncol = 1, strip.position = "right") +
    scale_x_continuous(breaks = seq(0, 100, by = 10)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.02), limits = c(0, 0.1)) +
    labs(title = labs["title"], x = labs["x"], y = labs["y"], caption = labs["caption"]) +
    theme_thesis(plot_margin = 15, design = THEME_DESIGN) +
    NULL

# saving ---
if (SAVE) {save_plot(filename = filename, width = width, height = height, dpi = RESOLUTION_DPI)}

# reset ---
rm(filename, height, labs, tmp, width)
```